---
title: "Assignment 1- 2"
author: "Simon"
date: "5/10/2021"
output: html_document
---


```{r}
library(tidyverse) # Collection of all the good stuff like dplyr, ggplot2 ect.
library(magrittr) # For extra-piping operators (eg. %<>%)'
library(threejs)
library(tidygraph)
library(ggraph)
```

```{r}
attr <- read_csv('https://raw.githubusercontent.com/SDS-AAU/SDS-master/master/00_data/network_krackhard/Krack-High-Tec-Attributes.csv') 

edge_ad = read.table("https://raw.githubusercontent.com/SDS-AAU/SDS-master/master/00_data/network_krackhard/Krack-High-Tec-edgelist-Advice.txt")

edge_f = read.table("https://raw.githubusercontent.com/SDS-AAU/SDS-master/master/00_data/network_krackhard/Krack-High-Tec-edgelist-Friendship.txt")

edge_r = read.table("https://raw.githubusercontent.com/SDS-AAU/SDS-master/master/00_data/network_krackhard/Krack-High-Tec-edgelist-ReportsTo.txt")


```
# Cleaning and EDA

```{r}
attr %>%  head()

attr %>% glimpse()
```


We know the following: 

- **ID**: Numeric ID of the manager
- **AGE**: The managers age (in years)
- **TENURE**: The length of service or tenure (in years)
- **LEVEL**: The level in the corporate hierarchy (coded 1,2 and 3; 1 = CEO, 2 = Vice President, 3 = manager)
- **DEPT**: The department (coded 1,2,3,4 with the CEO in department 0, ie not in a department)

So we will transform the **LEVEL** column so we have strings. 

```{r}
##attr %<>%
  ##mutate(LEVEL = recode(LEVEL, "1" = "CEO", "2" = "Vice President", "3" = "Manager"))

```

(Hvis vi køre koden over virker assortiativity for "LEVEL" ik)

# Create a network: 

Networks are created using igraph
```{r}
net_ad = graph_from_data_frame(d = edge_ad, vertices = attr, directed = T)
tg_net_ad= tbl_graph(edges = edge_ad, nodes = attr, directed = T)
```

```{r}
net_f = graph_from_data_frame(d = edge_f, vertices = attr, directed = T)
tg_net_f= tbl_graph(edges = edge_f, nodes = attr, directed = T)
```

```{r}
net_r = graph_from_data_frame(d = edge_r, vertices = attr, directed = T)
tg_net_r= tbl_graph(edges = edge_r, nodes = attr, directed = T)
```


# Analysis

Filtering for true observations in our edgelist.
```{r}
g_ad <- tg_net_ad %E>%
  filter(V3 == 1) %E>%
  select(!V3)

g_f <- tg_net_f %E>%
  filter(V3 == 1) %E>%
  select(!V3)

g_r <- tg_net_r %E>%
  filter(V3 == 1) %E>%
  select(!V3)
```

## A

**Network level characteristics. Find the overal network level of:**

**Density**

```{r}
edge_density(g_ad)

edge_density(g_f)

edge_density(g_r)
```


**Transitivity**

```{r}
transitivity(g_ad, type = "global")

transitivity(g_f, type = "global")

transitivity(g_r, type = "global")
```


**Resciprocity**

```{r}
reciprocity(g_ad)

reciprocity(g_f)

reciprocity(g_r)
```

## B Node level characteristics: Likewise, find out:



### 1. Who is most popular in the networks. Who is the most wanted friend, and advice giver?

We can find out who is the most important in the network by calculating the centrality in the networks.
We first calculate different centrality measures:
```{r}

## Advice
g_ad_cent <- g_ad %N>%
  mutate(cent_dgr_in = centrality_degree(mode = "in"),
         cent_dgr_out = centrality_degree(mode = "out"),
         cent_eig= centrality_eigen(directed = T),
         cent_between = centrality_betweenness(directed = T))

## Friends
g_f_cent <- g_f %N>%
  mutate(cent_dgr_in = centrality_degree(mode = "in"),
         cent_dgr_out = centrality_degree(mode = "out"),
         cent_eig= centrality_eigen(directed = T),
         cent_between = centrality_betweenness(directed = T))

```

#### Centrality degree

**Most central Advicer**

```{r}

## For "in"
g_ad_cent %N>%
  arrange(desc(cent_dgr_in))

```
We can see note two is the person with the largest Centrality when looking at people seeking him for advice. 

**Most central Friend**

```{r}

## For "in"

g_f_cent %N>%
  arrange(desc(cent_dgr_in))

```
Again we see ID 2 being the most central person when it comes to people seeing him as a friend. 


#### Centrality eigenvalue

**Most central Advicer**

```{r}
g_ad_cent %N>%
  arrange(desc(cent_eig))

```
Again we reach same conclusion

**Most central Friend**

```{r}

g_f_cent %N>%
  arrange(desc(cent_eig))

```
Again ID 2

#### Centrality betweeness

**Most central Advicer**

```{r}
g_ad_cent %N>%
  arrange(desc(cent_between))

```
ID 18 seems to be the most "central"

**Most central Friend**

```{r}

g_f_cent %N>%
  arrange(desc(cent_between))

```
ID 17 seems to be most central friend here. 


#### 2. Are managers in higher hirarchy more popular as friend, and advice giver?

We can look at the mean centrality score for each *LEVEL*:

**Betweeness**

```{r}

##Advice
g_ad_cent %N>%
  as_tibble() %>%
  group_by(LEVEL)%>%
  summarise(mean_between= mean(cent_between))

```
```{r}

##Friends
g_f_cent %N>%
  as_tibble() %>%
  group_by(LEVEL)%>%
  summarise(mean_between= mean(cent_between))

```

**Eigenvalue**

```{r}
g_ad_cent %N>%
  as_tibble() %>%
  group_by(LEVEL)%>%
  summarise(mean_eig= mean(cent_eig))

```


```{r}
g_f_cent %N>%
  as_tibble() %>%
  group_by(LEVEL)%>%
  summarise(mean_eig= mean(cent_eig))

```
Seems like overall Vice precidents seems to be the people that gets asked the most for advice, and seen as friends. 

## C Relational Characteristics: Answer the following questions:

#### Are managers from the same 1. department, or on the same 2. hirarchy, 3. age, or 4. tenuere more likely to become friends or give advice? (hint: assortiativity related)

**Are managers from the same department likely to become friends or give advice?**

```{r}
##Advice
assortativity(g_ad, V(g_ad)$DEPT, directed = TRUE)
```
Not that high

```{r}
##Friends
assortativity(g_f, V(g_f)$DEPT, directed = TRUE)
```

**Are managers from the same hirarchy likely to become friends or give advice?**

```{r}
##Advice
assortativity(g_ad, V(g_ad)$LEVEL, directed = TRUE)
```
Not that high

```{r}
##Friends
assortativity(g_f, V(g_f)$LEVEL, directed = TRUE)
```
**Are managers from the same age likely to become friends or give advice?**

```{r}
##Advice
assortativity(g_ad, V(g_ad)$AGE, directed = TRUE)
```
Not that high

```{r}
##Friends
assortativity(g_f, V(g_f)$AGE, directed = TRUE)
```
**Are managers from the same tenuere likely to become friends or give advice?**

```{r}
##Advice
assortativity(g_ad, V(g_ad)$TENURE, directed = TRUE)
```
Not that high

```{r}
##Friends
assortativity(g_f, V(g_f)$TENURE, directed = TRUE)
```
Damn its negative!


#### Are friends more likely to give each others advice?

idk

# Visualizations

We can visualizies all the networks at once: 




