---
title: "Assignment 1- 2"
author: "Simon"
date: "5/10/2021"
output: html_document
---


```{r}
library(tidyverse) # Collection of all the good stuff like dplyr, ggplot2 ect.
library(magrittr) # For extra-piping operators (eg. %<>%)'
library(threejs)
library(tidygraph)
library(ggraph)
```

```{r}
attr <- read_csv('https://raw.githubusercontent.com/SDS-AAU/SDS-master/master/00_data/network_krackhard/Krack-High-Tec-Attributes.csv') 

edge_ad = read.table("https://raw.githubusercontent.com/SDS-AAU/SDS-master/master/00_data/network_krackhard/Krack-High-Tec-edgelist-Advice.txt")

edge_f = read.table("https://raw.githubusercontent.com/SDS-AAU/SDS-master/master/00_data/network_krackhard/Krack-High-Tec-edgelist-Friendship.txt")

edge_r = read.table("https://raw.githubusercontent.com/SDS-AAU/SDS-master/master/00_data/network_krackhard/Krack-High-Tec-edgelist-ReportsTo.txt")


```
# Cleaning and EDA

```{r}
attr %>%  head()

attr %>% glimpse()
```


We know the following: 

- **ID**: Numeric ID of the manager
- **AGE**: The managers age (in years)
- **TENURE**: The length of service or tenure (in years)
- **LEVEL**: The level in the corporate hierarchy (coded 1,2 and 3; 1 = CEO, 2 = Vice President, 3 = manager)
- **DEPT**: The department (coded 1,2,3,4 with the CEO in department 0, ie not in a department)

So we will transform the **LEVEL** column so we have strings. 

```{r}
##attr %<>%
  ##mutate(LEVEL = recode(LEVEL, "1" = "CEO", "2" = "Vice President", "3" = "Manager"))

```

(Hvis vi køre koden over virker assortiativity for "LEVEL" ik)

# Create a network: 

Networks are created using igraph
```{r}
net_ad = graph_from_data_frame(d = edge_ad, vertices = attr, directed = T)
tg_net_ad= tbl_graph(edges = edge_ad, nodes = attr, directed = T)
```

```{r}
net_f = graph_from_data_frame(d = edge_f, vertices = attr, directed = T)
tg_net_f= tbl_graph(edges = edge_f, nodes = attr, directed = T)
```

```{r}
net_r = graph_from_data_frame(d = edge_r, vertices = attr, directed = T)
tg_net_r= tbl_graph(edges = edge_r, nodes = attr, directed = T)
```


# Analysis

Filtering for true observations in our edgelist.
```{r}
g_ad <- tg_net_ad %E>%
  filter(V3 == 1) %E>%
  select(!V3)

g_f <- tg_net_f %E>%
  filter(V3 == 1) %E>%
  select(!V3)

g_r <- tg_net_r %E>%
  filter(V3 == 1) %E>%
  select(!V3)
```

## A

**Network level characteristics. Find the overal network level of:**

**Density**

```{r}
edge_density(g_ad)

edge_density(g_f)

edge_density(g_r)
```


**Transitivity**

```{r}
transitivity(g_ad, type = "global")

transitivity(g_f, type = "global")

transitivity(g_r, type = "global")
```


**Resciprocity**

```{r}
reciprocity(g_ad)

reciprocity(g_f)

reciprocity(g_r)
```

## B Node level characteristics: Likewise, find out:



### 1. Who is most popular in the networks. Who is the most wanted friend, and advice giver?

We can find out who is the most important in the network by calculating the centrality in the networks.
We first calculate different centrality measures:
```{r}

## Advice
g_ad_cent <- g_ad %N>%
  mutate(cent_dgr_in = centrality_degree(mode = "in"),
         cent_dgr_out = centrality_degree(mode = "out"),
         cent_eig= centrality_eigen(directed = T),
         cent_between = centrality_betweenness(directed = T))

## Friends
g_f_cent <- g_f %N>%
  mutate(cent_dgr_in = centrality_degree(mode = "in"),
         cent_dgr_out = centrality_degree(mode = "out"),
         cent_eig= centrality_eigen(directed = T),
         cent_between = centrality_betweenness(directed = T))

```

#### Centrality degree

**Most central Advicer**

```{r}

## For "in"
g_ad_cent %N>%
  arrange(desc(cent_dgr_in))

```
We can see note two is the person with the largest Centrality when looking at people seeking him for advice. 

**Most central Friend**

```{r}

## For "in"

g_f_cent %N>%
  arrange(desc(cent_dgr_in))

```
Again we see ID 2 being the most central person when it comes to people seeing him as a friend. 


#### Centrality eigenvalue

**Most central Advicer**

```{r}
g_ad_cent %N>%
  arrange(desc(cent_eig))

```
Again we reach same conclusion

**Most central Friend**

```{r}

g_f_cent %N>%
  arrange(desc(cent_eig))

```
Again ID 2

#### Centrality betweeness

**Most central Advicer**

```{r}
g_ad_cent %N>%
  arrange(desc(cent_between))

```
ID 18 seems to be the most "central"

**Most central Friend**

```{r}

g_f_cent %N>%
  arrange(desc(cent_between))

```
ID 17 seems to be most central friend here. 


#### 2. Are managers in higher hirarchy more popular as friend, and advice giver?

We can look at the mean centrality score for each *LEVEL*:

**Betweeness**

```{r}

##Advice
g_ad_cent %N>%
  as_tibble() %>%
  group_by(LEVEL)%>%
  summarise(mean_between= mean(cent_between))

```
```{r}

##Friends
g_f_cent %N>%
  as_tibble() %>%
  group_by(LEVEL)%>%
  summarise(mean_between= mean(cent_between))

```

**Eigenvalue**

```{r}
g_ad_cent %N>%
  as_tibble() %>%
  group_by(LEVEL)%>%
  summarise(mean_eig= mean(cent_eig))

```


```{r}
g_f_cent %N>%
  as_tibble() %>%
  group_by(LEVEL)%>%
  summarise(mean_eig= mean(cent_eig))

```
Seems like overall Vice precidents seems to be the people that gets asked the most for advice, and seen as friends. 

## C Relational Characteristics: Answer the following questions:

#### Are managers from the same 1. department, or on the same 2. hirarchy, 3. age, or 4. tenuere more likely to become friends or give advice? (hint: assortiativity related)

**Are managers from the same department likely to become friends or give advice?**

```{r}
##Advice
assortativity(g_ad, V(g_ad)$DEPT, directed = TRUE)
```
Not that high

```{r}
##Friends
assortativity(g_f, V(g_f)$DEPT, directed = TRUE)
```

**Are managers from the same hirarchy likely to become friends or give advice?**

```{r}
##Advice
assortativity(g_ad, V(g_ad)$LEVEL, directed = TRUE)
```
Not that high

```{r}
##Friends
assortativity(g_f, V(g_f)$LEVEL, directed = TRUE)
```
**Are managers from the same age likely to become friends or give advice?**

```{r}
##Advice
assortativity(g_ad, V(g_ad)$AGE, directed = TRUE)
```
Not that high

```{r}
##Friends
assortativity(g_f, V(g_f)$AGE, directed = TRUE)
```
**Are managers from the same tenuere likely to become friends or give advice?**

```{r}
##Advice
assortativity(g_ad, V(g_ad)$TENURE, directed = TRUE)
```
Not that high

```{r}
##Friends
assortativity(g_f, V(g_f)$TENURE, directed = TRUE)
```
Damn its negative!


#### Are friends more likely to give each others advice?


```{r}
cor(edge_ad %>% pull(V3), 
    edge_f %>% pull(V3))
```


```{r}
graph.friendship_V2 <- g_f %E>% mutate(friends = which_mutual(g_f, es = E(g_f))) 

graph.friendship_V2 %E>% as.tibble() %>% count(friends)
```


```{r}
graph <- graph.friendship_V2 %E>% as_tibble() %>%
  left_join((g_ad %E>% as_tibble()), by = "from")%>%
  rename(to_friends= to.x, to_advice= to.y)
```



```{r}

## Not friends who gives advice to each other

graph_nf= graph %>%
filter(friends == F) %>%
  filter(to_friends == to_advice) %>%glimpse(width = 80) 

## Friends who gives advice to each other

graph_f = graph %>%
filter(friends == TRUE) %>%
  filter(to_friends == to_advice) %>%glimpse(width = 80) 

```


```{r}

#Number of friends who gives advice
f=count(graph_f)

#Numbber of not friends who gives advice
nf=count(graph_nf)
```

```{r}
#number of  people who are mutual friends 
total_f=graph.friendship_V2 %E>%
  as_tibble()%>%
  filter(friends == TRUE) %>%
  count()

# Number of people who are not mutual friends

total_nf=graph.friendship_V2 %E>%
  as_tibble()%>%
  filter(friends == F) %>%
  count()
```

```{r}
f/total_f*100

nf/total_nf*100
```
We take the amount of mutual friends, so if ID 1 sees ID 2 as a friend and ID 2 sees ID 1 as friend. (This will count as 2 observations) We then look if people who are mutual friends also give advice to eacch other, if ID 1 gives advice to ID 2 this will give 1 observation, and vice versa. (So not mutualy).

We then calculate the percantage of people who gives advice in a friendsship and outside a friendship. We see that it is almost the same so people who are friends are not more likely to give each others advice.

# Visualizations

We join the graphs

```{r}

g_ad = g_ad %E>% mutate(type= "advice")
g_f = g_f %E>% mutate(type= "friends")
g_r = g_r %E>% mutate(type= "respons")

# We could also join all the networks together.
g_all <- g_ad %>%
  graph_join(g_f, by = "ID") %>%
  graph_join(g_r, by = "ID")
```


```{r}
# Then we could plot them pointly via an edge facett...
g_all %>% 
  ggraph(layout = 'fr') + 
  geom_edge_fan(aes(col = type), ##The fan does so the edges will not overlay each other
                arrow = arrow(angle = 30, length = unit(0.25, 'cm'),type = "closed"), 
                alpha = 0.25) + 
  geom_node_point(col = 'pink') +
  geom_node_text(aes(label = ID)) + 
  theme_graph() +
  theme(legend.position = "none") +
  facet_edges(~type) ## Without the facet_edges we get one large plot where we can see the edges has different colors.
```


```{r}
g_f= g_f %N>% mutate(LEVEL = recode(LEVEL, "1" = "CEO", "2" = "Vice President", "3" = "Manager"))
```


```{r, fig.height= 7.5, fig.width=12.5}
set.seed(1337)
# Then we could plot them pointly via an edge facett...
g_f %N>% 
  filter(!node_is_isolated()) %>%
  ggraph(layout = 'stress') + 
  geom_edge_fan(arrow = arrow(angle = 30, length = unit(0.25, 'cm'),type = 'closed'), alpha = 0.25) + 
  geom_node_point(aes(col = LEVEL, size = centrality_eigen(directed = TRUE))) + ##WE color by different offices
  geom_node_text(aes(label = ID, size = centrality_eigen(directed = TRUE))) + 
  theme_graph() +
  theme(legend.position = "bottom") +
  facet_edges(~type)
```


